# Introduction {#intro}

`r if(identical(gitbook_on, FALSE))knitr::asis_output(paste0("This report is available as pdf and as an online interactive report at ", params$report_url, ". We recommend viewing online as the web-hosted html version contains more features and is more easily navigable."))`

`r if(identical(gitbook_on, FALSE)){knitr::asis_output("<br>")}`

## Line Breaks {-}
Here is an example of how to insert an empty line between paragraphs. We do it using two blank lines...

This is the paragraph that follows the empty line.

Additionally, writers should investigate the impacts of different header levels (ex. First level (#) or Second level
(##) or third (###)) as well as before and after figures/tables on spacing before and after the headers so we produce as
professional looking documents as possible.  There are idiosyncrasies with what happens for each above and below so that
should be tested by building the documents in both formats (`html` and `pdf`) and viewing the output. Here is a test
with a second level header with no empty line above and no empty line below.
## Header with no number {-}

It negates the header... wow.

If we put blank lines above the header however...

## Another numbered Header
No spacing or `<br>` above this line.  

Here is a `fpr_kable` with a cross reference to Table \@ref(tab:fpr-kable-nr).
```{r nice-tab, eval = TRUE}
knitr::kable(
  head(iris, 10), caption = 'Here is a nice kable!',
  booktabs = TRUE
)
```
This is what happens with multiple empty lines but no `<br>` inserted directly after a figure...


```{r fpr-kable-nr, eval = T}
head(iris, 20) %>% 
  fpr::fpr_kable(
  caption_text = 'Here is a fpr_kable with no cross-ref and the scroll set to not happen when pdf built.',
  scroll = gitbook_on)
```

<br>

But if we put a `<br>` below the figure with blank lines either side of our text we are good to go.

Test.


